---
title: "Using OBDBS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = F}
library(obdbs)
data_124$data <- dplyr::as_tibble(data_124$data)
```

OBDBS is the NEFSC observer program database. Details regarding the list of table and fields present can be found in the data [dictionary](http://nova.nefsc.noaa.gov/datadict/). To access any data you will need login credentials to the server and priviledges to access to the tables

## get_lengths

To obtain length data for a given species you will first need to connect to the database with your credentials
```{r login, echo=T , eval = F}
channel <- connect_to_database("nova","username")
```

Then you can get length data for say, american flounder (plaice), using its nespp3 code (124)
```{r get_length, echo=T , eval = F}
data_124 <- get_lengths(channel, species = "124", year = 1999)
```

or 

```{r get_length2, echo=T , eval = F}
data_124 <- get_lengths(channel, species = 124, year = 1999)
```

## Output

output from all functions will have the same form. A list containing three elements:

1. the data pull
2. the sql statement used in the pull
3. A list of all columns in the table. (Provided in case the user wishes to extend the query using `get_anything_sql`)

For example:

```{r sampledata, echo=T, eval= T }
# The data
data_124$data

# All column/field names in the table
data_124$colNames

# The sql statement
data_124$sql

```
